Individual Differenes

### 2023-09-03 Misc/indv_diff.qmd

indv_linpred <- e1_vxBMM |> linpred_draws(new_data_grid) |> 
  summarize(across(.linpred, lst(mean, sd, median), .names = "{.fn}"))

indv_epred <- e1_vxBMM |> epred_draws(new_data_grid) |>
  summarize(across(.epred, lst(mean, sd, median), .names = "{.fn}"))

indv_pred <- e1_vxBMM |> predicted_draws(new_data_grid) |>
   summarize(across(.prediction, lst(mean, sd, median), .names = "{.fn}"))

@@

  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope,SlopeInt,SlopeInt2, Intercept,b_Intercept,b_bandInt) |>
  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
    select(id,condit,condit_dummy,Intercept,b_Intercept,Slope,SlopeInt,SlopeInt2,b_bandInt, n) |>
  mutate(rankSlope=rank(Slope)) #|> arrange(rankSlope)   |> ungroup()

>>>>

# indv_linpred <- e1_vxBMM |> linpred_draws(new_data_grid) |> 
#   summarize(across(.linpred, lst(mean, sd, median), .names = "{.fn}"))
# 
# indv_epred <- e1_vxBMM |> epred_draws(new_data_grid) |>
#   summarize(across(.epred, lst(mean, sd, median), .names = "{.fn}"))
# 
# indv_pred <- e1_vxBMM |> predicted_draws(new_data_grid) |>
#    summarize(across(.prediction, lst(mean, sd, median), .names = "{.fn}"))

@@

  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope,SlopeInt,SlopeInt2, Intercept,b_Intercept,b_bandInt) |>
  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
    select(id,condit,condit_dummy,Intercept,b_Intercept,Slope,SlopeInt,SlopeInt2,b_bandInt, n) |>
  mutate(rankSlope=rank(Slope)) |> ungroup()  #|> arrange(rankSlope)   |> ungroup()
